---
title: "Twinned Cities"
execute: 
  eval: true
  echo: false
  warning: false
  message: false
---

```{=html}
<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/selectize.js/0.15.2/css/selectize.default.min.css">
<script src="https://cdnjs.cloudflare.com/ajax/libs/jquery/3.7.1/jquery.min.js"></script>
<script src="https://cdnjs.cloudflare.com/ajax/libs/selectize.js/0.15.2/js/selectize.min.js"></script>
```


```{r}
library(tidyverse)
library(showtext)
library(ggtext)
library(glue)
library(rcartocolor)
library(ggiraph)
library(colorTools)
library(htmltools)
cities_data <- read_csv("cities_data.csv")
```

```{r}
# Load fonts --------------------------------------------------------------

font_add_google("Oswald")
font_add_google("Nunito")
showtext_auto()
showtext_opts(dpi = 300)
title_font <- "Oswald"
body_font <- "Nunito"


# Define colours and fonts-------------------------------------------------

continents <- unique(cities_data$continent_col)
col_palette <- rcartocolor::carto_pal(n = length(continents) + 1, "Safe")[1:length(continents)]
names(col_palette) <- continents

bg_col <- "#FFFFFF"
text_col <- "#151C28"
highlight_col <- col_palette[1]
```

```{r}
region_data <- function(region, data) {
  output <- data |>
    group_by({{ region }}) |>
    mutate(n = n()) |>
    ungroup() |>
    select({{ region }}, n, continent_col, order, chosen_city) |>
    distinct() |>
    arrange(order)
  return(output)
}
```

```{r}
min_links <- 25
options_vec <- cities_data |>
  count(chosen_city) |> 
  filter(n >= min_links) |> 
  arrange(chosen_city) |>
  select(-n) |> 
  pull(chosen_city) 
names(options_vec) <- options_vec
default_name <- "Algiers"
dropdown_html <- tags$div(
  style = "text-align: center; margin-bottom: 10px;",
  tags$select(
    id = "dropdown",
    lapply(names(options_vec), function(name) {
      tags$option(
        value = options_vec[[name]],
        selected = if (name == default_name) "selected" else NULL,
        name
      )
    })
  )
)
```

```{r}
draw_layer <- function(pick_city) {
  output <- list(
    geom_col_interactive(
      data = filter(cities_data, chosen_city == pick_city) |>
        slice_head(n = 1),
      mapping = aes(
        x = 1, y = "0", fill = city_col,
        data_id = chosen_city
      ),
      position = "fill",
      width = 1
    ),
    geom_text_interactive(
      data = filter(cities_data, chosen_city == pick_city) |>
        slice_head(n = 1),
      mapping = aes(
        x = 0, y = "0", label = chosen_city,
        colour = blackOrWhite(col_palette[city_col]),
        data_id = chosen_city
      ),
      vjust = 2.8,
      size = 11,
      size.unit = "pt"
    ),
    geom_col_interactive(
      data = region_data(
        city,
        filter(cities_data, chosen_city == pick_city)
      ) |> 
        group_by(city, n, continent_col) |>
        slice_min(order) |>
        ungroup() |> 
        arrange(order) |> 
        mutate(city = factor(city, levels = city)),
      mapping = aes(
        x = n, y = "1", fill = continent_col,
        tooltip = city,
        data_id = chosen_city
      ),
      position = "fill",
      colour = text_col,
      width = 1
    ),
    geom_col_interactive(
      data = region_data(
        country,
        filter(cities_data, chosen_city == pick_city)
      ) |> 
        group_by(country, n, continent_col) |>
        slice_min(order) |>
        ungroup() |> 
        arrange(order) |> 
        mutate(country = factor(country, levels = country)),
      mapping = aes(
        x = n, y = "2", fill = continent_col,
        tooltip = country,
        data_id = chosen_city
      ),
      position = "fill",
      colour = text_col,
      width = 1
    ),
    geom_col_interactive(
      data = region_data(
        continent,
        filter(cities_data, chosen_city == pick_city)
      ) |>
        group_by(continent, n, continent_col) |>
        slice_min(order) |>
        ungroup() |>
        mutate(continent = factor(continent, levels = continent)),
      mapping = aes(
        x = n, y = "3", fill = continent_col,
        tooltip = continent,
        data_id = chosen_city
      ),
      position = "fill",
      colour = text_col,
      width = 1
    )
  )
  return(output)
}
```

```{r}
g_int <- ggplot() +
  scale_colour_identity() +
  scale_fill_manual(values = col_palette) +
  coord_radial(expand = FALSE) +
  theme_void(base_size = 12, base_family = body_font) +
  theme(
    legend.position = "none",
    plot.margin = margin(5, 5, 5, 5),
    plot.background = element_rect(fill = bg_col, colour = bg_col),
    panel.background = element_rect(fill = bg_col, colour = bg_col),
    panel.grid.minor = element_blank()
  )
for (i in 1:length(options_vec)) {
  g_int <- g_int +
  draw_layer(options_vec[i])
}
```

```{r}
g_girafe <- girafe(
  ggobj = g_int,
  bg = bg_col,
  options = list(
    opts_tooltip(
      delay_mouseover = 500,
      opacity = 0.9,
      css = glue("
        padding: 5pt;
        font-family: {body_font};
        font-size: 1rem;
        background-color: {bg_col};
        color: {text_col};
        border: solid;
        border-color: {text_col};
        border-radius: 5px;
        border-width: 2px")
    ),
    opts_hover(css = "opacity: 1;"),
    opts_hover_inv(css = "opacity: 0;"),
    opts_toolbar(hidden = c("saveaspng", "fullscreen")),
    opts_zoom(max = 1)
  )
)
```

Twinned towns (also known as sister cities) are a form of legal or social agreement between two geographically and politically distinct localities for the purpose of promoting cultural and commercial ties. This dataset looks at links specifically between cities, i.e. it does not include towns, villages or other geographic entities.

```{r}
#| output: asis
output <- purrr::map_chr(
  .x = 1:length(col_palette),
  .f = ~ glue("<span style='color:{col_palette[.x]}'>**{names(col_palette)[.x]}**</span>")
) |>
  stringr::str_flatten(collapse = ", ", last = ", and ")
cat(paste0("Select a city from the dropdown menu to see how it's connected across ", output, "."))
```


```{r}
browsable(
  tagList(
    dropdown_html,
    g_girafe
  )
)
```

```{css}
.selectize-input {
  border-radius: 4px !important;
  border: 2px solid #AAAAAA !important;
  padding: 4px 8px !important;
  background: white !important;
  box-shadow: none !important;
  text-align: left !important;
}

.selectize-dropdown {
  border: 2px solid #AAAAAA !important;
  border-radius: 4px !important;
  box-shadow: none !important;
  text-align: left !important;
}

.selectize-dropdown-content {
  max-height: 200px;
  overflow-y: auto;
}

.selectize-dropdown-content .option {
  padding: 4px 8px;
  cursor: pointer;
}

.selectize-dropdown-content .option:hover,
.selectize-dropdown-content .option.active {
  background: #f0f0f0 !important;
  color: inherit !important;
}
```

```{js}
$(document).ready(function() {
  $('#dropdown').selectize({
    maxOptions: 5500,
    onChange: function(value) {
      applySelection(value);
    }
  });

  setTimeout(function() {
    applySelection(document.getElementById('dropdown').value);
  }, 500);
});

function applySelection(value) {
  document.querySelectorAll('[data-id]').forEach(el => {
    if (el.getAttribute('data-id') === value) {
      el.setAttribute('style', 'display:block;');
    } else {
      el.setAttribute('style', 'display:none;');
    }
  });
}

```

**Note**: Only cities with at least `r min_links` connections are included in the dropdown.

**Data**: Wikidata (via [github.com/bothness/twin-cities](https://github.com/bothness/twin-cities))

**Graphic**: [Nicola Rennie](https://nrennie.rbind.io/)
